Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-24 ICLR25/relatedwork.tex

We compare {\CMP} with major verification tools for DNNs to clarify our methodology and its distinction from the existing state-of-the-art. CMP scales while preserving good accuracy, through targeting a limited number of binary variables based on compensating strength, stricking a good balance between exact encoding of a DNN using MILP~\cite{MILP} (too slow) and LP relaxation (too inaccurate). MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP encoding instead of CMP's many small encodings, which significantly reduce the number of binary variables necessary for each encoding. In \cite{DivideAndSlide}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more integer variables (thus runtime) to reach the same accuracy as our utility function (see Table \ref{tab:example1}), and restrict integer variables to the previous layer, which limits the accuracy reachable.

>>>>

We compare Hybrid MILP with major verification tools for DNNs to clarify our methodology and its distinction from the existing state-of-the-art. It scales while preserving good accuracy, through targeting a limited number of binary variables, stricking a good balance between exact encoding of a DNN using MILP~\cite{MILP} (too slow) and LP relaxation (too inaccurate). MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP encoding instead of Hybrid MILP's many small encodings, which significantly reduce the number of binary variables necessary for each encoding. In \cite{DivideAndSlide}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more integer variables (thus runtime) to reach the same accuracy as our utility function (see Table \ref{tab:example1}), and restrict integer variables to the previous layer, which limits the accuracy reachable.
